---
title: "Data607_Assingment05"
author: "Mahmud Hasan Al Raji"
date: "`r Sys.Date()`"
output: html_document
---


# Introduction: The pourpose of this assignment is to see the structures of data frame of a dataset wirtten in three different file formats: HTML,XML, and JSON.Here, a dataset on three books of interest have been created in three stated file formats and stored in github platform. Below are the file links: 


* HTML: https://raw.githubusercontent.com/Raji030/data_607_html/main/new0000%201.html 
* JSON: https://raw.githubusercontent.com/Raji030/myjsondata_607/main/data_607.json
* XML:  https://raw.githubusercontent.com/Raji030/data_607_xmlfile/main/data607.xml 




# Required Libraries

```{r }
library(XML)
library(plyr)
library(RCurl)
library(jsonlite)
```

# Converting HTML file to data frame

```{r }
myhtml_file<-getURL("https://raw.githubusercontent.com/Raji030/data_607_html/main/new0000%201.html")
myhtml_table<-readHTMLTable(myhtml_file)
myhtml_data<-as.data.frame(myhtml_table)
str(myhtml_data)
```

# Converting JSON the file to data frame 

```{r }
jsonfile<-fromJSON("https://raw.githubusercontent.com/Raji030/myjsondata_607/main/data_607.json")
myjson_data<-as.data.frame(jsonfile)
str(myjson_data)
```

# Converting XML file to data frame

```{r }
xmlfile<-getURL("https://raw.githubusercontent.com/Raji030/data_607_xmlfile/main/data607.xml")
xmllist<-xmlToList(xmlParse(xmlfile))
myxml_data <- ldply(xmllist, data.frame)
str(myxml_data)
```

# Conclusion: The data frames are not identical for the three file formats. For the HTML and JSON file formats,though, both the data frames contain 3 observations and 5 variables, but they are presenting their author cloumns' values in different class and ways. On the other hand, the XML file format contains data frame with 3 observations and 8 variables.That data frame has been created with splitting the 3 author names from one book into 3 different columns rather to showing the all 3 author names in a single column. Thus, each data frame has been created in diffrent layouts.



